Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-08-25 Supplemental-Material-A-Annotated-Analysis.Rmd
interaction follow-up stability added

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS2 <- dtS2Red %>% 
  select(TID, any_of(varNamS2MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         any_of(names(which(sapply(dtMiS2 %>% select(where(is.numeric)), sd, na.rm = TRUE) > 0)))) %>% # only vars that sd != 0
         #which(sapply(. %>% select(where(is.numeric)), sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

@@

```{r MiS1}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
set.seed(123)
MiS2 <-
  amelia(
    dtMiS2,
    m = 1, # 20
    ts = "TIDnum",
    cs = "PID",
    idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
    # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
    # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
    # leads = ...,
    # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
    # parallel = "multicore",
    # ncpus = parallel::detectCores(),
    p2s = 1
  )
save(MiS2, file = "data/imputed/S2Imputed.RData")
load("data/imputed/S2Imputed.RData")

@@

# # any interaction
# dtMiMain %>%
#   filter(is.na(InteractionDum) | InteractionDum != 0) %>%
#   #complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
#   nrow
# 
# # Intergroup Contact
# dtMiMain %>%
#   filter(is.na(IntergroupContact) | IntergroupContact != 0) %>%
#   #complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
#   nrow
# 
# # Ingroup Contact
# dtMiMain %>%
#   filter(is.na(IngroupContact) | IngroupContact != 0) %>%
#   #complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
#   nrow

```{r InteractionImp}
# TBD
```

@@

@@

>>>>

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS2 <- 
  dtS2Red %>% 
  select(TID, any_of(varNamS2MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  as.data.frame %>%
  mutate(date = as.character(date)) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  select_if(function(x) is.character(x) | (is.numeric(x) && sd(x) > 0)) %>%
         #which(sapply(. %>% select(where(is.numeric)), sd, na.rm = TRUE) > 0)) %>% # only vars that sd != 0
         #) %>% # only include variables that vary (i.e., sd != 0)
         #which(sd(., na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

@@

```{r MiS2}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS2 <-
#   amelia(
#     dtMiS2,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS2, file = "data/imputed/S2Imputed.RData")
#load("data/imputed/S2Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS2Stability <-
#   amelia(
#     dtMiS2,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS2Stability, file = "data/imputed/S2ImputedStability.RData")
#load("data/imputed/S2ImputedStability.RData")
```

@@

# any interaction
dtMiInteraction <- 
  dtMiMain %>%
    mutate_at(vars(any_of(varNamS123PCA), -any_of(idVars)), funs(ifelse(dtMiMain$InteractionDum != 1, NA, .))) %>%
    #mutate_at(vars(-any_of(idVars), -ends_with(".pre"), -ends_with(".post"), -InteractionDum), funs(ifelse(dtMiMain$InteractionDum != 1, NA, .))) %>%
    as.data.frame

# Intergroup Contact
dtMiIntergroup <- 
  dtMiMain %>%
  mutate_at(vars(any_of(varNamS123PCA), -any_of(idVars)), funs(ifelse(dtMiMain$IntergroupContact != 1, NA, .))) %>%
  #mutate_at(vars(-any_of(idVars), -ends_with(".pre"), -ends_with(".post"), -IntergroupContact), funs(ifelse(dtMiMain$IntergroupContact != 1, NA, .))) %>%
  #filter(is.na(relatednessNoInteraction)) %>%
  select(-relatednessNoInteraction) %>% # remove completely missing col
  as.data.frame

# dtMiIntergroup %>% 
#   select(ID, TIDnum, IntergroupContact, relatednessNoInteraction) %>%
#   arrange(ID, TIDnum, IntergroupContact)

# Ingroup Contact
dtMiIngroup <- 
  dtMiMain %>%
    #mutate_at(vars(any_of(varNamS123PCA), -any_of(idVars)), funs(ifelse(dtMiMain$IngroupContact != 1, NA, .))) %>%
    mutate_at(vars(-any_of(idVars), -ends_with(".pre"), -ends_with(".post"), -IngroupContact), funs(ifelse(dtMiMain$IngroupContact != 1, NA, .))) %>%
    as.data.frame
```

```{r InteractionImp}
#################################################################
##                       Any Interaction                       ##
#################################################################

##---------------------------------------------------------------
##                      Single Imputation                      --
##---------------------------------------------------------------
# set.seed(123)
# MiInteraction <-
#   amelia(
#     dtMiInteraction,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     #noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiInteraction, file = "data/imputed/InteractionImputed.RData")
load("data/imputed/InteractionImputed.RData")

##---------------------------------------------------------------
##                     Multiple Imputation                     --
##---------------------------------------------------------------

# # Stability to imputations:
# set.seed(123)
# MiInteractionStab <-
#   amelia(
#     dtMiInteraction,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     #noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiInteractionStab, file = "data/imputed/InteractionImputedStability.RData")
load("data/imputed/InteractionImputedStability.RData")
```

```{r intergroupImp}
##################################################################
##                    Intergroup Interaction                    ##
##################################################################

##---------------------------------------------------------------
##                      Single Imputation                      --
##---------------------------------------------------------------
# set.seed(123)
# MiIntergroup <-
#   amelia(
#     dtMiIntergroup,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact", "InteractionDum"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     #noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiIntergroup, file = "data/imputed/IntergroupImputed.RData")
load("data/imputed/IntergroupImputed.RData")

##---------------------------------------------------------------
##                     Multiple Imputation                     --
##---------------------------------------------------------------

# # Stability to imputations:
# set.seed(123)
# MiIntergroupStab <-
#   amelia(
#     dtMiIntergroup,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact", "InteractionDum"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     #noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiIntergroupStab, file = "data/imputed/IntergroupImputedStability.RData")
load("data/imputed/IntergroupImputedStability.RData")
```

```{r ingroupImp}
#################################################################
##                     Ingroup Interaction                     ##
##                        NOT CONVERGING                       ##
#################################################################

##---------------------------------------------------------------
##                      Single Imputation                      --
##---------------------------------------------------------------
# set.seed(123)
# MiIngroup <-
#   amelia(
#     dtMiIngroup,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact", "InteractionDum"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     #noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiIngroup, file = "data/imputed/IngroupImputed.RData")
# load("data/imputed/IngroupImputed.RData")

##---------------------------------------------------------------
##                     Multiple Imputation                     --
##---------------------------------------------------------------

# # Stability to imputations:
# set.seed(123)
# MiIngroupStab <-
#   amelia(
#     dtMiIngroup,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact", "InteractionDum"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     #noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiIngroupStab, file = "data/imputed/IngroupImputedStability.RData")
# load("data/imputed/IngroupImputedStability.RData")
```

@@

#### All Interaction Responses

```{r longToWideInteraction}

dtInteractionImpWide <- MiInteraction$imputations[[1]] %>% 
  select(ID, date, week, study, any_of(varNamS123PCA)) %>%
  arrange(ID, TIDnum) %>%
  filter(TIDnum <= min(max(dtS1Red$TIDnum), max(dtS2Red$TIDnum), max(dtS3Red$TIDnum))) %>%
  select(
    -TID,
    -date,
    -week
  ) %>%
  melt(
    .,
    id=c("ID", "TIDnum", "study")
  ) %>%
  mutate(
    variable = paste("T", stringr::str_pad(TIDnum, width = 2, pad = 0), "_", variable, sep = "")
  ) %>%
  select(-TIDnum, -study) %>%
  arrange(ID, variable) %>%
  pivot_wider(names_from = variable, values_from = value) %>%
  #replace(is.na(.), 0) %>%
  select(-ID)
```

```{r longToWidInteractionStability}
# Long to Wide Main Bi-daily
MiInteractionStabilityWide <- list()
for (i in 1:length(MiInteractionStab$imputations)) {
  MiInteractionStabilityWide[[i]] <-
    MiInteractionStab$imputations[[i]]  %>%
    # Variable selection
    select(ID, date, week, study, any_of(varNamS123PCA)) %>%
    # Sorting
    arrange(ID, TIDnum) %>%
    # Filter minimum common num of measurements
    filter(TIDnum <= min(
      max(dtS1Red$TIDnum), max(dtS2Red$TIDnum), max(dtS3Red$TIDnum)
    )) %>%
    # Rm unnecessary variables for restructuring
    select(-TID,
           -date,
           -week) %>%
    # Long to wide
    melt(.,
         id = c("ID", "TIDnum", "study")) %>%
    mutate(variable = paste(
      "T",
      stringr::str_pad(TIDnum, width = 2, pad = 0),
      "_",
      variable,
      sep = ""
    )) %>%
    select(-TIDnum, -study) %>%
    arrange(ID, variable) %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    #replace(is.na(.), 0) %>%
    select(-ID)
}
```

#### Intergroup Interaction Responses

```{r longToWideIntergroup}
dtIntergroupImpWide <- MiIntergroup$imputations[[1]] %>% 
  select(ID, date, week, study, any_of(varNamS123PCA)) %>%
  arrange(ID, TIDnum) %>%
  filter(TIDnum <= min(max(dtS1Red$TIDnum), max(dtS2Red$TIDnum), max(dtS3Red$TIDnum))) %>%
  select(
    -TID,
    -date,
    -week
  ) %>%
  melt(
    .,
    id=c("ID", "TIDnum", "study")
  ) %>%
  mutate(
    variable = paste("T", stringr::str_pad(TIDnum, width = 2, pad = 0), "_", variable, sep = "")
  ) %>%
  select(-TIDnum, -study) %>%
  arrange(ID, variable) %>%
  pivot_wider(names_from = variable, values_from = value) %>%
  #replace(is.na(.), 0) %>%
  select(-ID)
```

```{r longToWidIntergroupStability}
# Long to Wide Main Bi-daily
MiIntergroupStabilityWide <- list()
for (i in 1:length(MiIntergroupStab$imputations)) {
  MiIntergroupStabilityWide[[i]] <-
    MiIntergroupStab$imputations[[i]]  %>%
    # Variable selection
    select(ID, date, week, study, any_of(varNamS123PCA)) %>%
    # Sorting
    arrange(ID, TIDnum) %>%
    # Filter minimum common num of measurements
    filter(TIDnum <= min(
      max(dtS1Red$TIDnum), max(dtS2Red$TIDnum), max(dtS3Red$TIDnum)
    )) %>%
    # Rm unnecessary variables for restructuring
    select(-TID,
           -date,
           -week) %>%
    # Long to wide
    melt(.,
         id = c("ID", "TIDnum", "study")) %>%
    mutate(variable = paste(
      "T",
      stringr::str_pad(TIDnum, width = 2, pad = 0),
      "_",
      variable,
      sep = ""
    )) %>%
    select(-TIDnum, -study) %>%
    arrange(ID, variable) %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    #replace(is.na(.), 0) %>%
    select(-ID)
}
```

@@

#### All Interactions

```{r InteractionStabCZ}
##################################################################
##                  Center across Participants                  ##
##################################################################
MiInteractionStabilityWideC <- list()
for (i in 1:length(MiInteractionStabilityWide)) {
  MiInteractionStabilityWideC[[i]] <-
    ThreeWay::cent3(
      X = MiInteractionStabilityWide[[i]],
      # Nr. ppt.s (A)
      n = nrow(MiInteractionStabilityWide[[i]]),
      # Nr. variables (B)
      m = length(unique(sub("T[0-9]{2}_", "", names(MiInteractionStabilityWide[[i]])))),
      # Nr. time points (C)
      p = length(unique(sub("_.*", "", names(MiInteractionStabilityWide[[i]])))),
      # Center across Participants
      mode = 1
    ) %>%
    as.data.frame
}

##################################################################
##                 Normalize across Time Points                 ##
##################################################################
MiInteractionStabilityWideCZ <- list()
for (i in 1:length(MiInteractionStabilityWideC)) {
  MiInteractionStabilityWideCZ[[i]] <-
    ThreeWay::norm3(
      X = MiInteractionStabilityWideC[[i]], 
      # Nr. ppt.s (A)
      n = nrow(MiInteractionStabilityWideC[[i]]), 
      # Nr. variables (B)
      m = length(unique(sub("T[0-9]{2}_", "", names(MiInteractionStabilityWideC[[i]])))),
      # Nr. time points (C)
      p = length(unique(sub("_.*", "", names(MiInteractionStabilityWideC[[i]])))),
      # Normalize across Time Points
      mode = 2
    ) %>%
    as.data.frame
  names(MiInteractionStabilityWideCZ[[i]]) <- names(MiInteractionStabilityWideC[[i]])
}
```

```{r InteractionStabCompNum}

# Run PCA SUP to determine best combination
InteractionStabPcaSup <- list()
capture.output(
  for(i in 1:length(MiInteractionStabilityWideCZ)) {
    InteractionStabPcaSup[[i]] <- 
    ThreeWay::T3runsApproxFit(
    X = MiInteractionStabilityWideCZ[[i]], 
    n = nrow(MiInteractionStabilityWideCZ[[i]]), # Nr. ppt.s (A)
    m = length(unique(sub("T[0-9]{2}_", "", names(MiInteractionStabilityWideCZ[[i]])))), # Nr. variables (B)
    p = length(unique(sub("_.*", "", names(MiInteractionStabilityWideCZ[[i]])))), # Nr. time points (C)
    maxa = 20,
    maxb = 20,
    maxc = 20
  )
  }, 
file='NUL')

# Select Dimension Complexity
InteractionStabDimSelector <- list()
for (i in 1:length(InteractionStabPcaSup)) {
  InteractionStabDimSelector[[i]] <- capture.output(
    ThreeWay::DimSelector(
      out = InteractionStabPcaSup[[i]],
      n = nrow(MiInteractionStabilityWideCZ[[i]]), # Nr. ppt.s (A)
      m = length(unique(sub("T[0-9]{2}_", "", names(MiInteractionStabilityWideCZ[[i]])))), # Nr. variables (B)
      p = length(unique(sub("_.*", "", names(MiInteractionStabilityWideCZ[[i]])))), # Nr. time points (C)
      model = 2
    )
  )
}

InteractionStabDim <- list()
for (i in 1:length(InteractionStabDimSelector)) {
  InteractionStabDim[[i]] <-
    tail(InteractionStabDimSelector[[i]], n = 1) %>%
    str_extract("\\(.*\\)") %>%
    stringr::str_extract_all('\\d+', simplify = TRUE) %>%
    as.data.frame %>%
    mutate_all(as.numeric) %>%
    dplyr::rename(c(A = V1,
                    B = V2,
                    C = V3))
}

InteractionStabDim %>%
  bind_rows %>%
  as.data.frame %>%
  rownames_to_column(., var = "imputation") %>%
  group_by(A, B, C) %>%
  summarise(Frequency = n()) %>%
  arrange(-Frequency) %>%
  mutate(Percentage = formattable::percent(Frequency/sum(.$Frequency))) %>%
  kbl(
    .,
    escape = FALSE,
    booktabs = TRUE,
    align = "c",
    digits = 2,
    col.names = c(
      "Person",
      "Variable",
      "Time",
      "Frequency",
      "Percentage"
    ),
    caption = "Follow-up (Interactions): Frequency Table of Suggested Component Dimensions (from 20 imputed datasets)") %>%
  kable_classic(
    full_width = FALSE,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

#### Intergroup Interactions

```{r IntergroupStabCZ}
##################################################################
##                  Center across Participants                  ##
##################################################################
MiIntergroupStabilityWideC <- list()
for (i in 1:length(MiIntergroupStabilityWide)) {
  MiIntergroupStabilityWideC[[i]] <-
    ThreeWay::cent3(
      X = MiIntergroupStabilityWide[[i]],
      # Nr. ppt.s (A)
      n = nrow(MiIntergroupStabilityWide[[i]]),
      # Nr. variables (B)
      m = length(unique(sub("T[0-9]{2}_", "", names(MiIntergroupStabilityWide[[i]])))),
      # Nr. time points (C)
      p = length(unique(sub("_.*", "", names(MiIntergroupStabilityWide[[i]])))),
      # Center across Participants
      mode = 1
    ) %>%
    as.data.frame
}

##################################################################
##                 Normalize across Time Points                 ##
##################################################################
MiIntergroupStabilityWideCZ <- list()
for (i in 1:length(MiIntergroupStabilityWideC)) {
  MiIntergroupStabilityWideCZ[[i]] <-
    ThreeWay::norm3(
      X = MiIntergroupStabilityWideC[[i]], 
      # Nr. ppt.s (A)
      n = nrow(MiIntergroupStabilityWideC[[i]]), 
      # Nr. variables (B)
      m = length(unique(sub("T[0-9]{2}_", "", names(MiIntergroupStabilityWideC[[i]])))),
      # Nr. time points (C)
      p = length(unique(sub("_.*", "", names(MiIntergroupStabilityWideC[[i]])))),
      # Normalize across Time Points
      mode = 2
    ) %>%
    as.data.frame
  names(MiIntergroupStabilityWideCZ[[i]]) <- names(MiIntergroupStabilityWideC[[i]])
}
```

```{r IntergroupStabCompNum}

# Run PCA SUP to determine best combination
IntergroupStabPcaSup <- list()
capture.output(
  for(i in 1:length(MiIntergroupStabilityWideCZ)) {
    IntergroupStabPcaSup[[i]] <- 
    ThreeWay::T3runsApproxFit(
    X = MiIntergroupStabilityWideCZ[[i]], 
    n = nrow(MiIntergroupStabilityWideCZ[[i]]), # Nr. ppt.s (A)
    m = length(unique(sub("T[0-9]{2}_", "", names(MiIntergroupStabilityWideCZ[[i]])))), # Nr. variables (B)
    p = length(unique(sub("_.*", "", names(MiIntergroupStabilityWideCZ[[i]])))), # Nr. time points (C)
    maxa = 20,
    maxb = 20,
    maxc = 20
  )
  }, 
file='NUL')

# Select Dimension Complexity
IntergroupStabDimSelector <- list()
for (i in 1:length(IntergroupStabPcaSup)) {
  IntergroupStabDimSelector[[i]] <- capture.output(
    ThreeWay::DimSelector(
      out = IntergroupStabPcaSup[[i]],
      n = nrow(MiIntergroupStabilityWideCZ[[i]]), # Nr. ppt.s (A)
      m = length(unique(sub("T[0-9]{2}_", "", names(MiIntergroupStabilityWideCZ[[i]])))), # Nr. variables (B)
      p = length(unique(sub("_.*", "", names(MiIntergroupStabilityWideCZ[[i]])))), # Nr. time points (C)
      model = 2
    )
  )
}

IntergroupStabDim <- list()
for (i in 1:length(IntergroupStabDimSelector)) {
  IntergroupStabDim[[i]] <-
    tail(IntergroupStabDimSelector[[i]], n = 1) %>%
    str_extract("\\(.*\\)") %>%
    stringr::str_extract_all('\\d+', simplify = TRUE) %>%
    as.data.frame %>%
    mutate_all(as.numeric) %>%
    dplyr::rename(c(A = V1,
                    B = V2,
                    C = V3))
}

IntergroupStabDim %>%
  bind_rows %>%
  as.data.frame %>%
  rownames_to_column(., var = "imputation") %>%
  group_by(A, B, C) %>%
  summarise(Frequency = n()) %>%
  arrange(-Frequency) %>%
  mutate(Percentage = formattable::percent(Frequency/sum(.$Frequency))) %>%
  kbl(
    .,
    escape = FALSE,
    booktabs = TRUE,
    align = "c",
    digits = 2,
    col.names = c(
      "Person",
      "Variable",
      "Time",
      "Frequency",
      "Percentage"
    ),
    caption = "Follow-up (Intergroup Interactions): Frequency Table of Suggested Component Dimensions (from 20 imputed datasets)") %>%
  kable_classic(
    full_width = FALSE,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```
